---
title: "Explotary Analysis"
author: "R Coders"
date: "December 16, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, warning=FALSE}
#required packages
install.packages("tidyverse", repos = "https://cran.r-project.org")
install.packages("dplyr", repos = "https://cran.r-project.org")
install.packages("readxl", repos = "http://cran.us.r-project.org")
install.packages("ggplot2", repos = "http://cran.us.r-project.org")
install.packages("plotly", repos = "http://cran.us.r-project.org")
install.packages("gapminder", repos = "http://cran.us.r-project.org")
#install.packages("xlsx", repos = "http://cran.us.r-project.org")
install.packages("sqldf", repos = "http://cran.us.r-project.org")




library("tidyverse")
library("readxl")
library("ggplot2")
library("plotly")
library("gapminder")
#library("xlsx")
library("sqldf")
library("dplyr")
```

#### Download RDS Data from Github Page
Download export, import, USD Rate and Inflation rds files and put them in temp files and read them.  
And remove the temp files after reading.

```{r, warning=FALSE}
tmp<-tempfile(fileext=".rds")
download.file("https://github.com/MEF-BDA503/gpj18-r_coders/blob/master/Data_Sources_Rds/imp_data_final.rds?raw=true?raw=true",destfile=tmp,mode = 'wb')
imp_data_final<-read_rds(tmp)
file.remove(tmp)


tmp<-tempfile(fileext=".rds")
download.file("https://github.com/MEF-BDA503/gpj18-r_coders/blob/master/Data_Sources_Rds/exp_data_final.rds?raw=true?raw=true",destfile=tmp,mode = 'wb')
exp_data_final<-read_rds(tmp)
file.remove(tmp)


tmp<-tempfile(fileext=".rds")
download.file("https://github.com/MEF-BDA503/gpj18-r_coders/blob/master/Data_Sources_Rds/imp_data.rds?raw=true?raw=true",destfile=tmp,mode = 'wb')
imp_data<-read_rds(tmp)
file.remove(tmp)


tmp<-tempfile(fileext=".rds")
download.file("https://github.com/MEF-BDA503/gpj18-r_coders/blob/master/Data_Sources_Rds/exp_data.rds?raw=true?raw=true",destfile=tmp,mode = 'wb')
exp_data<-read_rds(tmp)
file.remove(tmp)

tmp<-tempfile(fileext=".rds")
download.file("https://github.com/MEF-BDA503/gpj18-r_coders/blob/master/Data_Sources_Rds/Producer_Inflation.rds?raw=true?raw=true",destfile=tmp,mode = 'wb')
producer_inf<-read_rds(tmp)
file.remove(tmp)

# Create a temporary file
tmp=tempfile(fileext=".xls")
# Download file from repository to the temp file
download.file("https://github.com/MEF-BDA503/gpj18-r_coders/blob/master/Data_Sources_Excel/export_import_sectors.xls?raw=true",destfile=tmp,mode='wb')
# Read that excel file.
sectors <- read_excel(tmp)
# Remove the temp file
file.remove(tmp)

tmp<-tempfile(fileext=".rds")
download.file("https://github.com/MEF-BDA503/gpj18-r_coders/blob/master/Data_Sources_Rds/US_Dollar_Montly_Rate.rds?raw=true?raw=true",destfile=tmp,mode = 'wb')
usd_rate<-read_rds(tmp)
file.remove(tmp)
```



Format Data
```{r, warning=FALSE}
names(exp_data_final)[names(exp_data_final) == 'Date'] <- 'Export_Date'
names(exp_data)[names(exp_data) == 'Date'] <- 'Export_Date'
names(imp_data_final)[names(imp_data_final) == 'Date'] <- 'Import_Date'
names(imp_data_final)[names(imp_data_final) == 'Export_Total_Amount'] <- 'Import_Total_Amount' #fix
names(imp_data)[names(imp_data) == 'Date'] <- 'Import_Date'


library("dplyr")
exp_data <- inner_join(exp_data,sectors, by=c("Sector_Type_Code"="Sub_Sector_Type_Code"))

imp_data <- inner_join(imp_data,sectors, by=c("Sector_Type_Code"="Sub_Sector_Type_Code"))

exp_data$Export_Year<-as.numeric(format(exp_data$Export_Date,"%Y"))
exp_data$Export_Year_Month<-format(exp_data$Export_Date,"%Y-%m")
exp_data_final$Export_Year<-as.numeric(format(exp_data_final$Export_Date,"%Y"))
exp_data_final$Export_Year_Month<-format(exp_data_final$Export_Date,"%Y-%m")

imp_data$Import_Year<-as.numeric(format(imp_data$Import_Date,"%Y"))
imp_data$Import_Year_Month<-format(imp_data$Import_Date,"%Y-%m")
imp_data_final$Import_Year<-as.numeric(format(imp_data_final$Import_Date,"%Y"))
imp_data_final$Import_Year_Month<-format(imp_data_final$Import_Date,"%Y-%m")

imp_data<- imp_data %>%
  select (Import_Date,Sector_Type_Code,Sector_Type_Code.y,Main_Sector_Flag,Sector_Name_Eng,Amount,Import_Year,Import_Year_Month)
  

exp_data<- exp_data %>%
  select (Export_Date,Sector_Type_Code,Sector_Type_Code.y,Main_Sector_Flag,Sector_Name_Eng, Amount,Export_Year,Export_Year_Month)  



colnames(imp_data)[colnames(imp_data) == 'Amount'] <- 'Import_Amount'
colnames(exp_data)[colnames(exp_data) == 'Amount'] <- 'Export_Amount'
colnames(imp_data)[colnames(imp_data) == 'Sector_Type_Code'] <- 'Sub_Sector_Type_Code'
colnames(exp_data)[colnames(exp_data) == 'Sector_Type_Code'] <- 'Sub_Sector_Type_Code'
colnames(imp_data)[colnames(imp_data) == 'Sector_Type_Code.y'] <- 'Sector_Type_Code'
colnames(exp_data)[colnames(exp_data) == 'Sector_Type_Code.y'] <- 'Sector_Type_Code'
imp_data$Import_Amount[is.na(imp_data$Import_Amount)] <- 0
imp_data_final$Import_Total_Amount[is.na(imp_data_final$Import_Total_Amount)] <- 0
exp_data$Export_Amount[is.na(exp_data$Export_Amount)] <- 0
exp_data_final$Export_Total_Amount[is.na(exp_data_final$Export_Total_Amount)] <- 0


exp_data_final <- exp_data_final %>%
  filter(Export_Date<'2018-11-01')

exp_data <- exp_data %>%
  filter(Export_Date<'2018-11-01')

imp_data_final <- imp_data_final %>%
  filter(Import_Date<'2018-11-01')

imp_data <- imp_data %>%
  filter(Import_Date<'2018-11-01')

saveRDS(imp_data,file="imp_data_v2.rds")
saveRDS(imp_data_final,file="imp_data_final_v2.rds")
saveRDS(exp_data,file="exp_data_v2.rds")
saveRDS(exp_data_final,file="exp_data_final_v2.rds")
```


Review Import Data Structure

```{r, warning=FALSE }
str(imp_data)
str(imp_data_final)
```

Review Export Data Structure

```{r, warning=FALSE }
str(exp_data)
str(exp_data_final)
```

Prepare Data for Import&Export Line Graph

```{r, warning=FALSE }
imp_and_exp_data <- inner_join(exp_data, imp_data, by=c("Export_Date" = "Import_Date","Sub_Sector_Type_Code"="Sub_Sector_Type_Code"))

imp_and_exp_data_bymonth <- aggregate(cbind(Import_Amount, Export_Amount) ~ Export_Date, data = imp_and_exp_data, sum)
imp_and_exp_data_bymonth <- gather(imp_and_exp_data_bymonth,
                               value = "value",
                               key = "type",
                               Export_Amount, Import_Amount)

#Rename column names
colnames(imp_and_exp_data_bymonth) <- c("Date","Type","Amount")

#Remove Empty Dates
imp_and_exp_data_bymonth <- imp_and_exp_data_bymonth %>%
  filter(Date<'2018-11-01')
```

## Export and Import Amount

The graph shows the year-based comparison of export and import amount data. A very long period of
increases and decreases are moving synchronously. In April 2018, the import amount Line has a major
decline, while export amount Line has a major increase.

```{r, warning=FALSE }
 p<-ggplot(imp_and_exp_data_bymonth,
        aes(x=Date,
            y=Amount/1000,
            color=Type)) +
   geom_line()+
   scale_size_area("Nitrogen") + 
   xlab("Import/Export Date") +
   ylab("Amount  (Million $)") +
   ggtitle("Import & Export Amount")
 style(p, text = row.names(imp_and_exp_data_bymonth))
```


## Export Amount Based on Consumer Price Index and USD Rate

The graph shows export amount based on consumer price index and USD rate on monthly basis. Each
year is indicated in different colors and every point shows monthly variables values.

```{r, warning=FALSE}
 
p <- exp_data_final %>%
  ggplot(aes(USD_Rate, Export_Total_Amount, size = Consumer_Price_Index_Yearly_Change, color=Export_Year)) +
  geom_point() +
  scale_x_log10() +
  theme_bw()+
  scale_size_area("Nitrogen") + 
  xlab("USD Rate") +
  ylab("Export Amount(1000$)") +
  ggtitle("Export Amounts and Consumer Price Index")

ggplotly(p)
```


```{r, warning=FALSE}
p <-
  plot_ly(data = exp_data_final, x = exp_data_final$Consumer_Price_Index_Yearly_Change, y = exp_data_final$Export_Total_Amount, size = exp_data_final$Consumer_Price_Index_Yearly_Change, color=exp_data_final$Export_Year,text = ~paste('Export Date:', exp_data_final$Export_Date, '<br>USD Rate:', exp_data_final$USD_Rate,
                                                                                                                                                                                                                                         '<br>Consumer Price Index Yearly Change:', exp_data_final$Consumer_Price_Index_Yearly_Change,
                                                                                                                                                                                                                                         '<br>Consumer Price Index Monthly Change:', exp_data_final$Consumer_Price_Index_Monthly_Change,
                                                                                                                                                                                                                                         '<br>Export Amount:', exp_data_final$Export_Total_Amount))  %>%
  layout(title = 'Export Amounts and  Consumer Price Index',
         xaxis = list(title =  'Consumer Price Index',
                      gridcolor = 'rgb(255, 255, 255)',
                      type = 'log',
                      zerolinewidth = 1,
                      ticklen = 5,
                      gridwidth = 2),
         yaxis = list(title ='Export Amount',
                      gridcolor = 'rgb(255, 255, 255)',
                      zerolinewidth = 1,
                      ticklen = 5,
                      gridwith = 2),
         paper_bgcolor = 'rgb(243, 243, 243)',
         plot_bgcolor = 'rgb(243, 243, 243)')

ggplotly(p)
```


## Import Amount Based on Consumer Price Index and USD Rate

The graph shows import amount based on consumer price index and USD rate on monthly basis. Each
year is indicated in different colors and every point shows monthly variables values.

```{r, warning=FALSE }
p <-
  plot_ly(data = imp_data_final, x = imp_data_final$Consumer_Price_Index_Yearly_Change, y = imp_data_final$Import_Total_Amount, size = imp_data_final$Consumer_Price_Index_Yearly_Change, color=imp_data_final$Import_Year,text = ~paste('Import Date:', imp_data_final$Import_Date, '<br>USD Rate:', imp_data_final$USD_Rate,
'<br>Consumer Price Index Yearly Change:', imp_data_final$Consumer_Price_Index_Yearly_Change,
'<br>Consumer Price Index Monthly Change:', imp_data_final$Consumer_Price_Index_Monthly_Change,
'<br>Import Amount:', imp_data_final$Import_Total_Amount))  %>%
  layout(title = 'Import Amounts and Consumer Price Index',
         xaxis = list(title =  'Consumer Price Index',
                      gridcolor = 'rgb(255, 255, 255)',
                      type = 'log',
                      zerolinewidth = 1,
                      ticklen = 5,
                      gridwidth = 2),
         yaxis = list(title ='Import Amount',
                      gridcolor = 'rgb(255, 255, 255)',
                      zerolinewidth = 1,
                      ticklen = 5,
                      gridwith = 2),
         paper_bgcolor = 'rgb(243, 243, 243)',
         plot_bgcolor = 'rgb(243, 243, 243)')

ggplotly(p)
```




```{r, warning=FALSE }
top_import_by_sector <-
  imp_data %>%
  filter(Main_Sector_Flag==1)%>% #& Import_Year==2018) %>%
  group_by(Import_Year,Sector_Type_Code,Sector_Name_Eng) %>%
  summarise(Import_Total_Amount=sum(Import_Amount))%>%
  arrange(desc(Import_Total_Amount)) 



top_export_by_sector <-
  exp_data %>%
  filter(Main_Sector_Flag==1)%>% #& Export_Year==2018) %>%
  group_by(Export_Year,Sector_Type_Code,Sector_Name_Eng) %>%
  summarise(Export_Total_Amount=sum(Export_Amount))%>%
  arrange(desc(Export_Total_Amount)) 

trade_deficit_by_sectors<-sqldf('select Export_Year as Year, a.Sector_Type_Code, 
a.Sector_Name_Eng, Export_Total_Amount, Import_Total_Amount,
(Import_Total_Amount - Export_Total_Amount) as Trade_Deficit_Amount 
    from top_export_by_sector a left join top_import_by_sector b
      on Export_Year = Import_Year
      and a.Sector_Type_Code = b.Sector_Type_Code')

trade_deficit_by_sectors$Import_Total_Amount[is.na(trade_deficit_by_sectors$Import_Total_Amount)] <- 0
trade_deficit_by_sectors$Trade_Deficit_Amount[is.na(trade_deficit_by_sectors$Trade_Deficit_Amount)] <- 0
```


#### Top sectors for Export
```{r, warning=FALSE }
head(top_export_by_sector)
```


#### Top sectors for Import
```{r, warning=FALSE }
head(top_import_by_sector)
```

## Yearly Trade Deficit Amount

Yearly trade deficit amount graph was prepared based on the sector. In general, there is a constant
decline. Although a clear result can not be seen due to the incomplete year for 2018, we can see that the
year will be closed down again for two months due to the close of the year.

```{r, warning=FALSE }
trade_deficit_by_sectors %>% 
  #filter(Main_Sector_Flag==1)%>%
  group_by(Year,Sector_Name_Eng) %>%
  summarise(Yearly_Total_Trade_Deficit_Amount=sum(Trade_Deficit_Amount))%>%
  ggplot(data = ., aes(x = Year, y = Yearly_Total_Trade_Deficit_Amount, 
                       fill = Sector_Name_Eng)) + geom_bar(stat = "identity", position=position_dodge()) + aes(x = Year, y =   Yearly_Total_Trade_Deficit_Amount) + labs(x = "", y = "", title = "Yearly Trade Deficit Amount") + theme_bw() +  scale_y_continuous(labels = scales::comma) +   guides(fill=guide_legend(title="Sectors"))+
  xlab("Year") +
  ylab("Amount(1000$)")
```  


### Preparation Data for Yearly Average Export Amount and Other Factors
```{r, warning=FALSE }
library("dplyr")
exp_data_total_amount_by_year <-
  exp_data %>%
  group_by(Export_Date,Export_Year) %>%
  summarise(Yearly_Export_Total_Amount=sum(Export_Amount))

exp_data_amount_and_others <- inner_join(exp_data_final,exp_data_total_amount_by_year, by=c("Export_Date" = "Export_Date"))
#str(exp_data_amount_and_others) for test

exp_data_amount_and_others$Export_Year.x <- as.numeric(as.character(exp_data_amount_and_others$Export_Year.x))
#str(exp_data_amount_and_others) for test

colnames(exp_data_amount_and_others)[colnames(exp_data_amount_and_others) == 'Export_Year.x'] <- 'Export_Year'

  exp_data_amount_and_others_yearly <-  
  exp_data_amount_and_others %>%
  group_by(Export_Year) %>%
  summarise(Yearly_Avg_Export_Amount=mean(Yearly_Export_Total_Amount),
            Yearly_Avg_Consumer_Price_Index_Yearly_Change = mean(Consumer_Price_Index_Yearly_Change),
            Yearly_Avg_Consumer_Price_Index_Monthly_Change = mean(Consumer_Price_Index_Monthly_Change),
            Yearly_Avg_USD_Rate = mean(USD_Rate))

head(exp_data_amount_and_others)
```  

## Yearly Average Export Amount and Other Factors

Yearly average export amount and other factors show the inflation rate of the points in the chart. At
every point can be seen yearly average USD rate, yearly average export amount, yearly average
consumer price index yearly change.

```{r, warning=FALSE }
#Export_Yearly_Avg_Values  
library("ggplot2")
library("plotly")
  p <- exp_data_amount_and_others_yearly %>%
    ggplot(aes(Yearly_Avg_USD_Rate, Yearly_Avg_Export_Amount, size = Yearly_Avg_Consumer_Price_Index_Yearly_Change, color=Export_Year)) +
    geom_point() +
    scale_x_log10() +
    theme_bw()+
    xlab("USD Rate") +
    ylab("Export Amount(1000$)") +
    ggtitle("Yearly Average Export Amount and Other Factors")
  
  ggplotly(p)
```    

#### Minimum, Maximum, Average and Total Export Amounts by Sectors and Years

```{r, warning=FALSE }
exp_min_max_mean_by_sectors<- exp_data %>% 
  filter(Main_Sector_Flag==1)%>% 
  group_by(Export_Year,Sector_Name_Eng) %>% 
  summarise_each(funs(min(.,na.rm=TRUE), round(mean(.,na.rm=TRUE),digits = 3), max(.,na.rm=TRUE),sum(.,na.rm=TRUE)),Export_Amount)

head(exp_min_max_mean_by_sectors)
```   


## Export Sector Share

The graph shows the sector shares in the total export amount. Only one sector is above the sector
average export amount. 
Manufacturing export amount is higher than the total of the other sector import
amounts.

```{r, warning=FALSE }
exp_share_sectors <- 
  exp_data  %>% 
  filter(Main_Sector_Flag==1 & Export_Date<'2018-11-01')%>% 
  group_by(Sector_Name_Eng) %>%
  summarize(Export_Amount_Share=sum(Export_Amount)) %>%
  mutate (Export_Amount_Share=round((Export_Amount_Share/sum(Export_Amount_Share)),4))


exp_share_sectors$share_z <- round((exp_share_sectors$Export_Amount_Share - mean(exp_share_sectors$Export_Amount_Share))/sd(exp_share_sectors$Export_Amount_Share), 2)

exp_share_sectors$above_or_below <- ifelse(exp_share_sectors$share_z < 0, "Below", "Above")  
exp_share_sectors <- exp_share_sectors[order(exp_share_sectors$share_z), ]
exp_share_sectors$Sector_Name_Eng <- factor(exp_share_sectors$Sector_Name_Eng, levels = exp_share_sectors$Sector_Name_Eng)


theme_set(theme_bw())

ggplot(exp_share_sectors, aes(x= share_z   , y=  Sector_Name_Eng, label=share_z)) + 
  xlab("Z") +
  ylab("Sector Name") +
  ggtitle("Export Sector Share")+
  geom_point(stat='identity', aes(col=above_or_below), size=6) #+
```   


## Import Sector Share

The graph shows the sector shares in the total import amount. Only two sector is above the sector
average import amount because of that manufacturing is extremely higher than other sectors. Mining is
also important but manufacturing import amount is higher than the total of the other sector import
amounts.

```{r, warning=FALSE }
imp_share_sectors <- 
  imp_data  %>% 
  filter(Main_Sector_Flag==1 & Import_Date<'2018-11-01')%>% 
  group_by(Sector_Name_Eng) %>%
  summarize(Import_Amount_Share=sum(Import_Amount)) %>%
  mutate (Import_Amount_Share=round((Import_Amount_Share/sum(Import_Amount_Share)),4))


imp_share_sectors$share_z <- round((imp_share_sectors$Import_Amount_Share - mean(imp_share_sectors$Import_Amount_Share))/sd(imp_share_sectors$Import_Amount_Share), 2)

imp_share_sectors$above_or_below <- ifelse(imp_share_sectors$share_z < 0, "Below", "Above")  
imp_share_sectors <- imp_share_sectors[order(imp_share_sectors$share_z), ]
imp_share_sectors$Sector_Name_Eng <- factor(imp_share_sectors$Sector_Name_Eng, levels = imp_share_sectors$Sector_Name_Eng)


 theme_set(theme_bw())
 
 ggplot(imp_share_sectors, aes(x= share_z   , y=  Sector_Name_Eng, label=share_z)) + 
   xlab("Z") +
   ylab("Sector Name") +
   ggtitle("Import Sector Share")+
   geom_point(stat='identity', aes(col=above_or_below), size=6)
```


## Export Amount by Sectors and Year  

The graph shows the export amounts by sectors and years. We can see that manufacturing is the main
part of the export amount. Manufacturing export amount is sharply increased between 2010-2013 and it
is in a cycle of increase-decrease-stable for every 3 year between 2013-2018.

```{r, warning=FALSE}
exp_agg_by_sectors<- exp_data %>% 
  filter(Main_Sector_Flag==1)%>% 
  group_by(Export_Year,Sector_Name_Eng,Sector_Type_Code) %>% 
  summarise_each(funs(min(.,na.rm=TRUE), round(mean(.,na.rm=TRUE),digits = 3), max(.,na.rm=TRUE),sum(.,na.rm=TRUE)),Export_Amount)


colnames(exp_agg_by_sectors)<- c("Export_Year", "Sector_Name_Eng","Sector_Type_Code", "Min_Amount", "Avg_Amount", "Max_Amount", "Total_Amount" )
``` 

```{r, warning=FALSE}
p <- exp_agg_by_sectors %>%
    ggplot(aes(x = Export_Year, y= Total_Amount, group=Min_Amount, group2 = Max_Amount,
               group3 = Sector_Name_Eng, size = Avg_Amount, color=Sector_Type_Code)) +
    geom_point() +
    scale_x_log10() +
    theme_bw()+
    scale_size_area("Nitrogen") + 
    xlab("Export Year") +
    ylab("Export Amount(1000$)") +
    ggtitle("Export Amount by Sectors and Years")

  
ggplotly(p)
``` 

```{r, warning=FALSE}
library("tidyverse")
library("plotly")
p1 <- plot_ly(data = exp_agg_by_sectors, x = exp_agg_by_sectors$Export_Year, y = exp_agg_by_sectors$Total_Amount, color = exp_agg_by_sectors$Sector_Type_Code, size = exp_agg_by_sectors$Total_Amount, colors = NULL ,sizes = c(10, 100), 
              type = 'scatter', mode = 'markers',marker = list(symbol = 'circle', sizemode = 'diameter',line = list(width = 1, color = '#FFFFFF')),
              text = ~paste('Sector Name:',exp_agg_by_sectors$Sector_Name_Eng,
'<br>Export Year:', exp_agg_by_sectors$Export_Year, '<br>Total Export Amount:', exp_agg_by_sectors$Total_Amount,
                            '<br>Min Export Amount:', exp_agg_by_sectors$Min_Amount,
                            '<br>Max Export Amount:', exp_agg_by_sectors$Max_Amount,
                            '<br>Avg Export Amount:', exp_agg_by_sectors$Avg_Amount)) %>%
  layout(title = 'Export Amount by Sectors and Year',
         xaxis = list(title =  'Export Year',
                      gridcolor = 'rgb(255, 255, 255)',
                      type = 'log',
                      zerolinewidth = 1,
                      ticklen = 5,
                      gridwidth = 2),
         yaxis = list(title ='Total Export Amount',
                      gridcolor = 'rgb(255, 255, 255)',
                      zerolinewidth = 1,
                      ticklen = 5,
                      gridwith = 2),
         paper_bgcolor = 'rgb(243, 243, 243)',
         plot_bgcolor = 'rgb(243, 243, 243)')

p1
```


## Import Amount by Sectors and Year  

The graph shows import amounts by sectors and years. Manufacturing is the main port of our import.
Mining amounts gives us a chance to compare manufacturing amounts and mining amount trends. We
can see that there is almost a synchronization between manufacturing and mining trends which may
mean overall factors affects these two sectors in the same way and with a nearly equal rate.

```{r, warning=FALSE}
imp_agg_by_sectors<- imp_data %>% 
  filter(Main_Sector_Flag==1)%>% 
  group_by(Import_Year,Sector_Name_Eng,Sector_Type_Code) %>% 
  summarise_each(funs(min(.,na.rm=TRUE), round(mean(.,na.rm=TRUE),digits = 3), max(.,na.rm=TRUE),sum(.,na.rm=TRUE)),Import_Amount)


colnames(imp_agg_by_sectors)<- c("Import_Year", "Sector_Name_Eng","Sector_Type_Code", "Min_Amount", "Avg_Amount", "Max_Amount", "Total_Amount" )
 
library("tidyverse")
library("plotly")
p1 <- plot_ly(data = imp_agg_by_sectors, x = imp_agg_by_sectors$Import_Year, y = imp_agg_by_sectors$Total_Amount, color = imp_agg_by_sectors$Sector_Type_Code, size = imp_agg_by_sectors$Total_Amount, colors = NULL ,sizes = c(10, 100), 
              type = 'scatter', mode = 'markers',marker = list(symbol = 'circle', sizemode = 'diameter',line = list(width = 1, color = '#FFFFFF')),
              text = ~paste('Sector Name:',imp_agg_by_sectors$Sector_Name_Eng,
                            '<br>Import Year:', imp_agg_by_sectors$Import_Year, '<br>Total Import Amount:', imp_agg_by_sectors$Total_Amount,
                            '<br>Min Import Amount:', imp_agg_by_sectors$Min_Amount,
                            '<br>Max Import Amount:', imp_agg_by_sectors$Max_Amount,
                            '<br>Avg Import Amount:', imp_agg_by_sectors$Avg_Amount)) %>%
  layout(title = 'Import Amount by Sectors and Year',
         xaxis = list(title =  'Import Year',
                      gridcolor = 'rgb(255, 255, 255)',
                      type = 'log',
                      zerolinewidth = 1,
                      ticklen = 5,
                      gridwidth = 2),
         yaxis = list(title ='Total Import Amount',
                      gridcolor = 'rgb(255, 255, 255)',
                      zerolinewidth = 1,
                      ticklen = 5,
                      gridwith = 2),
         paper_bgcolor = 'rgb(243, 243, 243)',
         plot_bgcolor = 'rgb(243, 243, 243)')

p1
```



## Export Amount based on USD Rate and Inflation

The graph shows export amounts, USD rate and inflation. First thing that take attention is USD rate is
increasing slowly or fast but it is always increasing however export amount and inflation is fluctuated by
years. Export amount and inflation is nearly synchronized. If we look at 2014-2016 USD rate is increasing
and export amount is decreased significantly however in 2016-2018 USD rate is increasing again and
export amount is increased significantly which means that only USD rate is not enough to explain
direction and fluctuations in export amounts.

```{r, warning=FALSE }
colors = c("red", "blue", "green")

# Set the margins of the plot wider
par(oma = c(0, 2, 2, 3))

plot(exp_data_final$Export_Date, exp_data_final$Export_Total_Amount, yaxt = "n", xlab = "Export Date", main = "Export Amount & USD Rate & Inflation", 
     ylab = "")
lines(exp_data_final$Export_Date, exp_data_final$Export_Total_Amount)

# We use the "pretty" function go generate nice axes
axis(at = pretty(exp_data_final$Export_Total_Amount), side = 2)
library("tidyverse")
exp_data_final <- exp_data_final %>%
  select(Export_Date,Export_Total_Amount,USD_Rate,Consumer_Price_Index_Yearly_Change
         ,Consumer_Price_Index_Monthly_Change,Export_Year,Export_Year_Month)

str(exp_data_final)
# The side for the axes.  The next one will go on 
# the left, the following two on the right side
sides <- list(2, 4, 4) 

# The number of "lines" into the margin the axes will be
lines <- list(2, NA, 2)


for(i in 3:5) {
  par(new = TRUE)
  plot(exp_data_final$Export_Date, exp_data_final[[i]], axes = FALSE, col = colors[i - 1], xlab = "", ylab = "")
  axis(at = pretty(exp_data_final[[i]]), side = sides[[i-2]], line = lines[[i-2]], 
       col = colors[i - 1])
  #mtext(2,text=colnames(exp_data_final)[i],line=2)
  lines(exp_data_final$Export_Date, exp_data_final[[i]], col = colors[i - 1])
}
```

## Trade Deficit Amount by Sub Sector Names

```{r, warning=FALSE}
   emp_by_sectors <- exp_data %>%
   filter(Main_Sector_Flag == 0) %>%
   group_by(Sector_Name_Eng,Sub_Sector_Type_Code) %>%
   summarize(Total_Export_Amount = sum(Export_Amount))
 
   imp_by_sectors <- imp_data %>%
   filter(Main_Sector_Flag == 0) %>%
   group_by(Sector_Name_Eng,Sub_Sector_Type_Code) %>%
   summarize(Total_Import_Amount = sum(Import_Amount))
 
 trade_deficit_sub_sector <- inner_join(imp_by_sectors, emp_by_sectors, by =c("Sub_Sector_Type_Code", "Sub_Sector_Type_Code")) %>%
   mutate(Trade_Deficit_Amount = Total_Import_Amount - Total_Export_Amount)%>%
   arrange(desc(Trade_Deficit_Amount))

trade_deficit_sub_sector %>%
  ggplot(aes(x=reorder(Sector_Name_Eng.x, Trade_Deficit_Amount), 
             y=Trade_Deficit_Amount, color =Sector_Name_Eng.x, fill=Sector_Name_Eng.x)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  labs(x = "Sub Sector Name", y = "Trade Deficit Amount") +
  ggtitle("Trade Deficit by Sub Sectors") +
  theme(legend.position = "none", axis.text.x = element_text(angle = 0, vjust = 10.0, hjust = 0.0, size = 1))
``` 



## Trade Deficit Amount by Sub Sectors Codes

```{r, warning=FALSE}
   emp_by_sectors <- exp_data %>%
   filter(Main_Sector_Flag == 0) %>%
   group_by(Sector_Name_Eng,Sub_Sector_Type_Code) %>%
   summarize(Total_Export_Amount = sum(Export_Amount))
 
   imp_by_sectors <- imp_data %>%
   filter(Main_Sector_Flag == 0) %>%
   group_by(Sector_Name_Eng,Sub_Sector_Type_Code) %>%
   summarize(Total_Import_Amount = sum(Import_Amount))
 
 trade_deficit_sub_sector <- inner_join(imp_by_sectors, emp_by_sectors, by =c("Sub_Sector_Type_Code", "Sub_Sector_Type_Code")) %>%
   mutate(Trade_Deficit_Amount = Total_Import_Amount - Total_Export_Amount)%>%
   arrange(desc(Trade_Deficit_Amount))

trade_deficit_sub_sector %>%
  ggplot(aes(x=reorder(Sub_Sector_Type_Code, Trade_Deficit_Amount), 
             y=Trade_Deficit_Amount, color =Sub_Sector_Type_Code, fill=Sub_Sector_Type_Code)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  labs(x = "Sub Sector Name", y = "Trade Deficit Amount") +
  ggtitle("Trade Deficit by Sub Sectors") +
  theme(legend.position = "none", axis.text.x = element_text(angle = 0, vjust = 10.0, hjust = 0.0, size = 1))
``` 

