---
title: "Explotary Analysis"
author: "R_Coders"
date: "December 20, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, warning=FALSE }
install.packages("tidyverse", repos = "https://cran.r-project.org")
install.packages("dplyr", repos = "https://cran.r-project.org")
install.packages("readxl", repos = "http://cran.us.r-project.org")
install.packages("ggplot2", repos = "http://cran.us.r-project.org")
install.packages("plotly", repos = "http://cran.us.r-project.org")
install.packages("gapminder", repos = "http://cran.us.r-project.org")
#install.packages("xlsx", repos = "http://cran.us.r-project.org")
install.packages("sqldf", repos = "http://cran.us.r-project.org")




library("tidyverse")
library("readxl")
library("ggplot2")
library("plotly")
library("gapminder")
#library("xlsx")
library("sqldf")
library("dplyr")
```


```{r, warning=FALSE }
tmp<-tempfile(fileext=".rds")
download.file("https://github.com/MEF-BDA503/gpj18-r_coders/blob/master/Data_Sources_Rds/imp_data_final.rds?raw=true?raw=true",destfile=tmp,mode = 'wb')
imp_data_final<-read_rds(tmp)
file.remove(tmp)


tmp<-tempfile(fileext=".rds")
download.file("https://github.com/MEF-BDA503/gpj18-r_coders/blob/master/Data_Sources_Rds/exp_data_final.rds?raw=true?raw=true",destfile=tmp,mode = 'wb')
exp_data_final<-read_rds(tmp)
file.remove(tmp)


tmp<-tempfile(fileext=".rds")
download.file("https://github.com/MEF-BDA503/gpj18-r_coders/blob/master/Data_Sources_Rds/imp_data.rds?raw=true?raw=true",destfile=tmp,mode = 'wb')
imp_data<-read_rds(tmp)
file.remove(tmp)


tmp<-tempfile(fileext=".rds")
download.file("https://github.com/MEF-BDA503/gpj18-r_coders/blob/master/Data_Sources_Rds/exp_data.rds?raw=true?raw=true",destfile=tmp,mode = 'wb')
exp_data<-read_rds(tmp)
file.remove(tmp)

tmp<-tempfile(fileext=".rds")
download.file("https://github.com/MEF-BDA503/gpj18-r_coders/blob/master/Data_Sources_Rds/Producer_Inflation.rds?raw=true?raw=true",destfile=tmp,mode = 'wb')
producer_inf<-read_rds(tmp)
file.remove(tmp)

# Create a temporary file
tmp=tempfile(fileext=".xls")
# Download file from repository to the temp file
download.file("https://github.com/MEF-BDA503/gpj18-r_coders/blob/master/Data_Sources_Excel/export_import_sectors.xls?raw=true",destfile=tmp,mode='wb')
# Read that excel file.
sectors <- read_excel(tmp)
# Remove the temp file
file.remove(tmp)

tmp<-tempfile(fileext=".rds")
download.file("https://github.com/MEF-BDA503/gpj18-r_coders/blob/master/Data_Sources_Rds/US_Dollar_Montly_Rate.rds?raw=true?raw=true",destfile=tmp,mode = 'wb')
usd_rate<-read_rds(tmp)
file.remove(tmp)
```



Format Data
```{r, warning=FALSE }
names(exp_data_final)[names(exp_data_final) == 'Date'] <- 'Export_Date'
names(exp_data)[names(exp_data) == 'Date'] <- 'Export_Date'
names(imp_data_final)[names(imp_data_final) == 'Date'] <- 'Import_Date'
names(imp_data_final)[names(imp_data_final) == 'Export_Total_Amount'] <- 'Import_Total_Amount' #fix
names(imp_data)[names(imp_data) == 'Date'] <- 'Import_Date'


library("dplyr")
exp_data <- inner_join(exp_data,sectors, by=c("Sector_Type_Code"="Sub_Sector_Type_Code"))

imp_data <- inner_join(imp_data,sectors, by=c("Sector_Type_Code"="Sub_Sector_Type_Code"))

exp_data$Export_Year<-as.numeric(format(exp_data$Export_Date,"%Y"))
exp_data$Export_Year_Month<-format(exp_data$Export_Date,"%Y-%m")
exp_data_final$Export_Year<-as.numeric(format(exp_data_final$Export_Date,"%Y"))
exp_data_final$Export_Year_Month<-format(exp_data_final$Export_Date,"%Y-%m")

imp_data$Import_Year<-as.numeric(format(imp_data$Import_Date,"%Y"))
imp_data$Import_Year_Month<-format(imp_data$Import_Date,"%Y-%m")
imp_data_final$Import_Year<-as.numeric(format(imp_data_final$Import_Date,"%Y"))
imp_data_final$Import_Year_Month<-format(imp_data_final$Import_Date,"%Y-%m")

imp_data<- imp_data %>%
  select (Import_Date,Sector_Type_Code,Sector_Type_Code.y,Main_Sector_Flag,Sector_Name_Eng,Amount,Import_Year,Import_Year_Month)
  

exp_data<- exp_data %>%
  select (Export_Date,Sector_Type_Code,Sector_Type_Code.y,Main_Sector_Flag,Sector_Name_Eng, Amount,Export_Year,Export_Year_Month)  



colnames(imp_data)[colnames(imp_data) == 'Amount'] <- 'Import_Amount'
colnames(exp_data)[colnames(exp_data) == 'Amount'] <- 'Export_Amount'
colnames(imp_data)[colnames(imp_data) == 'Sector_Type_Code'] <- 'Sub_Sector_Type_Code'
colnames(exp_data)[colnames(exp_data) == 'Sector_Type_Code'] <- 'Sub_Sector_Type_Code'
colnames(imp_data)[colnames(imp_data) == 'Sector_Type_Code.y'] <- 'Sector_Type_Code'
colnames(exp_data)[colnames(exp_data) == 'Sector_Type_Code.y'] <- 'Sector_Type_Code'
imp_data$Import_Amount[is.na(imp_data$Import_Amount)] <- 0
imp_data_final$Import_Total_Amount[is.na(imp_data_final$Import_Total_Amount)] <- 0
exp_data$Export_Amount[is.na(exp_data$Export_Amount)] <- 0
exp_data_final$Export_Total_Amount[is.na(exp_data_final$Export_Total_Amount)] <- 0


exp_data_final <- exp_data_final %>%
  filter(Export_Date<'2018-11-01')

exp_data <- exp_data %>%
  filter(Export_Date<'2018-11-01')

imp_data_final <- imp_data_final %>%
  filter(Import_Date<'2018-11-01')

imp_data <- imp_data %>%
  filter(Import_Date<'2018-11-01')

saveRDS(imp_data,file="imp_data_v2.rds")
saveRDS(imp_data_final,file="imp_data_final_v2.rds")
saveRDS(exp_data,file="exp_data_v2.rds")
saveRDS(exp_data_final,file="exp_data_final_v2.rds")
```



Review Import Data Structure
```{r, warning=FALSE }
str(imp_data)
str(imp_data_final)
```

Review Export Data Structure
```{r, warning=FALSE }
str(exp_data)
str(exp_data_final)
```

Prepare Data for Import&Export Line Graph
```{r, warning=FALSE }
imp_and_exp_data <- inner_join(exp_data, imp_data, by=c("Export_Date" = "Import_Date","Sub_Sector_Type_Code"="Sub_Sector_Type_Code"))

imp_and_exp_data_bymonth <- aggregate(cbind(Import_Amount, Export_Amount) ~ Export_Date, data = imp_and_exp_data, sum)
imp_and_exp_data_bymonth <- gather(imp_and_exp_data_bymonth,
                               value = "value",
                               key = "type",
                               Export_Amount, Import_Amount)

#Rename column names
colnames(imp_and_exp_data_bymonth) <- c("Date","Type","Amount")

#Remove Empty Dates
imp_and_exp_data_bymonth <- imp_and_exp_data_bymonth %>%
  filter(Date<'2018-11-01')
```

01_export_and_import_amount
```{r, warning=FALSE }
 p<-ggplot(imp_and_exp_data_bymonth,
        aes(x=Date,
            y=Amount/1000,
            color=Type)) +
   geom_line()+
   scale_size_area("Nitrogen") + 
   xlab("Import/Export Date") +
   ylab("Amount  (Million $)") +
   ggtitle("Import & Export Amount")
 style(p, text = row.names(imp_and_exp_data_bymonth))
```


02_Export_Amount_Based_on_Consumer_Price_Index_And_USD_Rate
```{r, warning=FALSE }
library(ggplot2)
library(plotly)
library(gapminder)
 
p <- exp_data_final %>%
  ggplot(aes(USD_Rate, Export_Total_Amount, size = Consumer_Price_Index_Yearly_Change, color=Export_Year)) +
  geom_point() +
  scale_x_log10() +
  theme_bw()+
  scale_size_area("Nitrogen") + 
  xlab("USD Rate") +
  ylab("Export Amount(1000$)") +
  ggtitle("Export Amounts and Consumer Price Index")

ggplotly(p)
```


03_Import_Amount_Based_on_Consumer_Price_Index_And_USD_Rate
```{r, warning=FALSE }
p <- imp_data_final %>%
  ggplot(aes(USD_Rate, Import_Total_Amount, size = Consumer_Price_Index_Yearly_Change, color=Import_Year)) +
  geom_point() +
  scale_x_log10() +
  theme_bw()+
  scale_size_area("Nitrogen") + 
  xlab("USD Rate") +
  ylab("Import Amount(1000$)") +
  ggtitle("Import Amounts and Consumer Price Index")

ggplotly(p)
```




```{r, warning=FALSE }
top_import_by_sector <-
  imp_data %>%
  filter(Main_Sector_Flag==1)%>% #& Import_Year==2018) %>%
  group_by(Import_Year,Sector_Type_Code,Sector_Name_Eng) %>%
  summarise(Import_Total_Amount=sum(Import_Amount))%>%
  arrange(desc(Import_Total_Amount)) 



top_export_by_sector <-
  exp_data %>%
  filter(Main_Sector_Flag==1)%>% #& Export_Year==2018) %>%
  group_by(Export_Year,Sector_Type_Code,Sector_Name_Eng) %>%
  summarise(Export_Total_Amount=sum(Export_Amount))%>%
  arrange(desc(Export_Total_Amount)) 

trade_deficit_by_sectors<-sqldf('select Export_Year as Year, a.Sector_Type_Code, 
a.Sector_Name_Eng, Export_Total_Amount, Import_Total_Amount,
(Import_Total_Amount - Export_Total_Amount) as Trade_Deficit_Amount 
    from top_export_by_sector a left join top_import_by_sector b
      on Export_Year = Import_Year
      and a.Sector_Type_Code = b.Sector_Type_Code')

trade_deficit_by_sectors$Import_Total_Amount[is.na(trade_deficit_by_sectors$Import_Total_Amount)] <- 0
trade_deficit_by_sectors$Trade_Deficit_Amount[is.na(trade_deficit_by_sectors$Trade_Deficit_Amount)] <- 0
```


04_yearly_trade_deficit_amount
```{r, warning=FALSE }
trade_deficit_by_sectors %>% 
  #filter(Main_Sector_Flag==1)%>%
  group_by(Year,Sector_Name_Eng) %>%
  summarise(Yearly_Total_Trade_Deficit_Amount=sum(Trade_Deficit_Amount))%>%
  ggplot(data = ., aes(x = Year, y = Yearly_Total_Trade_Deficit_Amount, 
                       fill = Sector_Name_Eng)) + geom_bar(stat = "identity", position=position_dodge()) + aes(x = Year, y =   Yearly_Total_Trade_Deficit_Amount) + labs(x = "", y = "", title = "Yearly Trade Deficit Amount") + theme_bw() +  scale_y_continuous(labels = scales::comma) +   guides(fill=guide_legend(title="Sectors"))+
  xlab("Year") +
  ylab("Amount(1000$)")
```  


Prepare Data for Yearly Average Export Amount and Other Factors
```{r, warning=FALSE }
library("dplyr")
exp_data_total_amount_by_year <-
  exp_data %>%
  group_by(Export_Date,Export_Year) %>%
  summarise(Yearly_Export_Total_Amount=sum(Export_Amount))

exp_data_amount_and_others <- inner_join(exp_data_final,exp_data_total_amount_by_year, by=c("Export_Date" = "Export_Date"))
str(exp_data_amount_and_others)

library("dplyr")
exp_data_amount_and_others$Export_Year.x <- as.numeric(as.character(exp_data_amount_and_others$Export_Year.x))
str(exp_data_amount_and_others)

colnames(exp_data_amount_and_others)[colnames(exp_data_amount_and_others) == 'Export_Year.x'] <- 'Export_Year'

  exp_data_amount_and_others_yearly <-  
  exp_data_amount_and_others %>%
  group_by(Export_Year) %>%
  summarise(Yearly_Avg_Export_Amount=mean(Yearly_Export_Total_Amount),
            Yearly_Avg_Consumer_Price_Index_Yearly_Change = mean(Consumer_Price_Index_Yearly_Change),
            Yearly_Avg_Consumer_Price_Index_Monthly_Change = mean(Consumer_Price_Index_Monthly_Change),
            Yearly_Avg_USD_Rate = mean(USD_Rate))

str(exp_data_amount_and_others)
```  

05-Yearly Average Export Amount and Other Factors
```{r, warning=FALSE }
#Export_Yearly_Avg_Values  
library("ggplot2")
library("plotly")
  p <- exp_data_amount_and_others_yearly %>%
    ggplot(aes(Yearly_Avg_USD_Rate, Yearly_Avg_Export_Amount, size = Yearly_Avg_Consumer_Price_Index_Yearly_Change, color=Export_Year)) +
    geom_point() +
    scale_x_log10() +
    theme_bw()+
    xlab("USD Rate") +
    ylab("Export Amount(1000$)") +
    ggtitle("Yearly Average Export Amount and Other Factors")
  
  ggplotly(p)
```    

```{r, warning=FALSE }
exp_min_max_mean_by_sectors<- exp_data %>% 
  filter(Main_Sector_Flag==1)%>% 
  group_by(Export_Year,Sector_Name_Eng) %>% 
  summarise_each(funs(min(.,na.rm=TRUE), round(mean(.,na.rm=TRUE),digits = 3), max(.,na.rm=TRUE),sum(.,na.rm=TRUE)),Export_Amount)

head(exp_min_max_mean_by_sectors)
```   


06_Export_Sector_Share
```{r, warning=FALSE }
exp_share_sectors <- 
  exp_data  %>% 
  filter(Main_Sector_Flag==1 & Export_Date<'2018-11-01')%>% 
  group_by(Sector_Name_Eng) %>%
  summarize(Export_Amount_Share=sum(Export_Amount)) %>%
  mutate (Export_Amount_Share=round((Export_Amount_Share/sum(Export_Amount_Share)),4))


exp_share_sectors$share_z <- round((exp_share_sectors$Export_Amount_Share - mean(exp_share_sectors$Export_Amount_Share))/sd(exp_share_sectors$Export_Amount_Share), 2)

exp_share_sectors$above_or_below <- ifelse(exp_share_sectors$share_z < 0, "Below", "Above")  
exp_share_sectors <- exp_share_sectors[order(exp_share_sectors$share_z), ]
exp_share_sectors$Sector_Name_Eng <- factor(exp_share_sectors$Sector_Name_Eng, levels = exp_share_sectors$Sector_Name_Eng)


theme_set(theme_bw())

ggplot(exp_share_sectors, aes(x= share_z   , y=  Sector_Name_Eng, label=share_z)) + 
  xlab("Share Z") +
  ylab("Sector Name") +
  ggtitle("Export Sector Share")+
  geom_point(stat='identity', aes(col=above_or_below), size=6) #+
```   


06_Import_Sector_Share
```{r, warning=FALSE }
imp_share_sectors <- 
  imp_data  %>% 
  filter(Main_Sector_Flag==1 & Import_Date<'2018-11-01')%>% 
  group_by(Sector_Name_Eng) %>%
  summarize(Import_Amount_Share=sum(Import_Amount)) %>%
  mutate (Import_Amount_Share=round((Import_Amount_Share/sum(Import_Amount_Share)),4))


imp_share_sectors$share_z <- round((imp_share_sectors$Import_Amount_Share - mean(imp_share_sectors$Import_Amount_Share))/sd(imp_share_sectors$Import_Amount_Share), 2)

imp_share_sectors$above_or_below <- ifelse(imp_share_sectors$share_z < 0, "Below", "Above")  
imp_share_sectors <- imp_share_sectors[order(imp_share_sectors$share_z), ]
imp_share_sectors$Sector_Name_Eng <- factor(imp_share_sectors$Sector_Name_Eng, levels = imp_share_sectors$Sector_Name_Eng)


 theme_set(theme_bw())
 
 ggplot(imp_share_sectors, aes(x= share_z   , y=  Sector_Name_Eng, label=share_z)) + 
   xlab("Share Z") +
   ylab("Sector Name") +
   ggtitle("Import Sector Share")+
   geom_point(stat='identity', aes(col=above_or_below), size=6)
```


07_Export_Amount_by_Sectors_And_Year
```{r, warning=FALSE }
exp_agg_by_sectors<- exp_data %>% 
  filter(Main_Sector_Flag==1)%>% 
  group_by(Export_Year,Sector_Name_Eng) %>% 
  summarise_each(funs(min(.,na.rm=TRUE), round(mean(.,na.rm=TRUE),digits = 3), max(.,na.rm=TRUE),sum(.,na.rm=TRUE)),Export_Amount)


library(ggplot2)
library(plotly)
library(gapminder)

colnames(exp_agg_by_sectors)<- c("Export_Year", "Sector_Name_Eng", "Min_Amount", "Avg_Amount", "Max_Amount", "Total_Amount" )
 
p <- exp_agg_by_sectors %>%
    ggplot(aes(x = Export_Year, y= Total_Amount, group=Min_Amount, group2 = Max_Amount, size = Avg_Amount, color=Sector_Name_Eng)) +
    geom_point() +
    scale_x_log10() +
    theme_bw()+
    scale_size_area("Nitrogen") + 
    xlab("Export Year") +
    ylab("Export Amount(1000$)") +
    ggtitle("Export Amount by Sectors and Years")

  
ggplotly(p)
  
```



